The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-02-14 paper/ms.tex
lambda errors

We use the full width at half maximum (FWHM) to quantify the line
broadening. Figure \ref{fig:widthvsvelocity} shows how the FWHM increases
with rotational velocity both for the central an homogeneous source
distributions.  We parameterize the dependency of the line width as
\begin{equation}
 {\rm FWHM}^2 = {\rm FWHM}_{0}^2 + V_{\rm max}^2/\lambda^2,
\label{eq:fwhm}
\end{equation}
%
where FWHM$_{0}$ is the
velocity width in the static case and $\lambda$ is a positive scalar
to be determined as a fit to the data. With this test we want to know
to what extent the new velocity width can be expressed as a quadratic
sum of the two relevant velocities in the problem. We fit
simultaneously all the points corresponding to central and homogeneous
models to find $\lambda_{\rm c} = 3.9 \pm 3.17\times 10^{-17}$ and $\lambda_{\rm h}=
1.9\pm 3.07\times 10^{-10}$ respectively.  {\bf EL ERROR ES de $10^{-17}???$}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.90\textwidth]{f11.eps}
\end{center}
\caption{Triple peaked profiles for three different off-center positions
  $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid
  line) and for different rotational velocities.  
   \label{fig:3p_profiles}} 
\end{figure*}

@@

We also explore the effects of off-centered emission in the line
morphology. Figure \ref{fig:OC_profiles} show the spectra for the two
off-centered emitting spheres located at $C=\pm0.5R$.  In this case we
only use photons that have outgoing directions aligned with the
observer i.e. $0.9 <\vert \mu \vert < 1.0$. We do not find any strong
asymmetry in the line morphology.

>>>>

We use the full width at half maximum (FWHM) to quantify the line
broadening. Figure \ref{fig:widthvsvelocity} shows how the FWHM increases
with rotational velocity both for the central an homogeneous source
distributions.  We parameterize the dependency of the line width as
\begin{equation}
 {\rm FWHM}^2 = {\rm FWHM}_{0}^2 + V_{\rm max}^2/\lambda^2,
\label{eq:fwhm}
\end{equation}
%
where FWHM$_{0}$ is the
velocity width in the static case and $\lambda$ is a positive scalar
to be determined as a fit to the data. With this test we want to know
to what extent the new velocity width can be expressed as a quadratic
sum of the two relevant velocities in the problem. We fit
simultaneously all the points corresponding to central and homogeneous
models to find $\lambda_{\rm c} = 3.9 \pm 0.041$ and $\lambda_{\rm h}=
1.9\pm 0.062$ respectively.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.90\textwidth]{f11.eps}
\end{center}
\caption{Triple peaked profiles for three different off-center positions
  $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid
  line) and for different rotational velocities. And $\theta$ represents the angle 
  between the rotation axes $\hat{k}$ and the observer line of sight.
   \label{fig:3p_profiles}} 
\end{figure*}

@@

We also explore the effects of the off-centered emission in the line
morphology. Figure \ref{fig:OC_profiles} show the spectra for the two
off-centered emitting spheres located at $C=\pm0.5R$.  In this case we
only use photons that have outgoing directions aligned with the
observer i.e. $0.9 <\vert \mu \vert < 1.0$. We do not find any strong
asymmetry in the line morphology.
